### 2021-01-25 README.Rmd
rebuilt README

```{r}
library(tidyverse)
library(forestecology)
library(sf)
library(sfheaders)
library(blockCV)
library(yardstick)
library(snakecase)
```

@@

# Visualizations
autoplot(comp_bayes_lm_ex, type = "intercepts")
autoplot(comp_bayes_lm_ex, type = "dbh_slopes")
autoplot(comp_bayes_lm_ex, type = "competition")
```

>>>>

```{r}
library(tidyverse)
library(forestecology)
library(sf)
library(sfheaders)
library(blockCV)
library(yardstick)
library(snakecase)
library(patchwork)
```

@@

# Visualizations (combined with patchwork pkg)
p1 <- autoplot(comp_bayes_lm_ex, type = "intercepts")
p2 <- autoplot(comp_bayes_lm_ex, type = "dbh_slopes")
p3 <- autoplot(comp_bayes_lm_ex, type = "competition")
(p1 | p2) / p3
```
